\documentclass{article}
\usepackage{hyperref}   % For clickable links in the PDF
\usepackage{verbatim}   % For verbatim code listings

\title{NovaBeamer Theme Documentation}
\author{Riccardo Martelli}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This document provides an overview and usage guide for the NovaBeamer Theme, a LaTeX template designed for elegant and iconic academic and scientific presentations. It explains installation, basic usage, customization options, and licensing details.
\end{abstract}

\section{Introduction}
The \textbf{NovaBeamer Theme} is a custom Beamer theme aimed at delivering a clean, minimalistic style suitable for academic and scientific presentations. This documentation outlines its features and guides users on how to get started.

\section{Installation}
To install the NovaBeamer Theme:
\begin{enumerate}
  \item Copy \texttt{novabeamer.sty} into your LaTeX working directory, or install it in your local/global LaTeX tree.
  \item Ensure that any dependent packages (e.g., \texttt{graphicx}, \texttt{xcolor}, \texttt{tikz}) are installed.
\end{enumerate}

\section{Usage Example}
Below is a simple example of a Beamer presentation using the NovaBeamer Theme:
\begin{verbatim}
\documentclass{beamer}
\usepackage{novabeamer}

\title{Sample Presentation}
\author{Your Name}
\institute{Your Institution}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}{Introduction}
Welcome to this presentation using the NovaBeamer Theme.
\end{frame}

\end{document}
\end{verbatim}

\section{Customization}
The NovaBeamer Theme offers several customizable features:
\begin{itemize}
  \item \textbf{Theme Colors:} Colors are defined with commands like \verb|\definecolor{...}|. For instance, the red tone is set with:
  \begin{verbatim}
  \definecolor{sithred}{RGB}{159,18,18}
  \end{verbatim}
  \item \textbf{Title Page Layout:} A custom title page is defined using a Beamer color box and TikZ for styling.
  \item \textbf{Frame Titles and Footers:} Custom templates for frame titles and footers allow further style adjustments.
\end{itemize}

\section{License}
This project is released under the \textbf{Unlicense License}, granting you complete freedom to use, modify, and distribute the NovaBeamer Theme. Please refer to the accompanying \texttt{LICENSE} file for full details.

\section{Additional Examples}
For more in-depth examples of how to use the NovaBeamer Theme, please refer to the example file (e.g., \texttt{novabeamer-example.tex}) available in the \texttt{examples/} directory.

\end{document}
